### 2015-02-10 src/3_TimeSeries.tex
unit rood finished

\[
y_t = \boldsymbol{\beta}^\top
\]

>>>>

\begin{equation}
\label{eq:adftest}
y_t = \boldsymbol{\beta}^\top \mathbb{D}_t + \phi y_{t-1} + \sum_{j=1}^p \Psi_j \Delta y_{t-j} + \epsilon_t
\end{equation}

\noindent where $\mathbb{D}_t$ is a vector of deterministic terms. Lag length $p$ has to be determined when applying the test, Akaike Information Criteria (AIC) is commonly used to determine it.
The p-lagged difference terms $\Delta y_{t-j}$ are used to approximate an ARMA process and the value of $p$ is set so that the error $\epsilon_t$ is serially uncorrelated. 
Under the null hypothesis, $y_t$ is I(1) which implies that $\phi=1$. 
The test statistic is the following:

\[
\text{ADF}_t = \frac{\hat{\phi} -1}{SE(\phi)}
\]

The $\text{ADF}_t$ statistic is based on the least squares estimates of equation \ref{eq:adftest}.
